---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(ggplot2)
library(dplyr)
```



# ppscore - a R implementation of the Predictive Power Score (PPS)

<!-- badges: start -->
<!-- badges: end -->


This in R port of the Predictive Power Score (PPS) developed by [8080Labs](https://github.com/8080labs/ppscore) for Python and described on the blog post [Toward Data Science](https://towardsdatascience.com/rip-correlation-introducing-the-predictive-power-score-3d90808b9598?gi=ba32980cd4d4).

As of June, 8080Labs developed an R version, [PPScoreR](https://github.com/8080labs/ppscoreR) which will likely be better maintained then this will.... so go use that.

This is also my first attempt at building a package... mostly for fun.  

## Installation

You can install via:

```{r eval = FALSE}
remotes::install_github("jlawren67/ppscore")
```

## PPScore

The `ppscore` function returns the Predictive Power Score for any target and feature.  The score represents how well the feature explains the target.

```{r example1}
library(ppscore)
## basic example code

titanic <- read.csv('https://raw.githubusercontent.com/8080labs/ppscore/master/examples/titanic.csv', stringsAsFactors = F)

ppscore(titanic, "Survived", "Sex")

```

## pps_matrix

To run comparisons on all variables in the data.frame, use the `pps_matrix` function.  This will run all possible target/feature combinations and return in a long-format data frame.

```{r example2, warning=FALSE,message=FALSE,error=FALSE}
mtx_check <- pps_matrix(titanic)

```

The PPS Matrix can then be generated by:
```{r plot}
mtx_check %>%
  filter(task_name %in% c('predict_itself', 'classification', 'regression')) %>%
  add_count(target, name = "appearance") %>%
  filter(appearance > 1) %>%
ggplot(aes(x = feature, y = target, fill = ppscore)) +
  geom_tile() +
  geom_text(aes(label = ppscore %>% round(2))) +
  scale_fill_viridis_c(guide = F)

```

